Online {\IterComp}

### 2017-09-14 results.tex
List margin
fix minor layout things in result figures; add WPO speedup results. other text restructuring

For comparison, we use four configurations\footnote{A configuration using the WPO relaxation was not used due to the time necessary for executing the experiments.}.
In all configurations, the same optimization sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimization sequence across distinct inputs.
The optimization sequences are ranked based on their average performance, and the best optimization sequence is selected.
%When selecting the best optimization sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}
\item \textbf{Oracle-RM} executes the program twice for each input, measuring the real speedup for each optimization sequence, and then uses the real speedup over {\flagstype -O0} for guiding online {\itercomp}. This oracle provides a reference results for assessing the effectiveness work-efficiency metric.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  It uses the work-efficiency metric for guiding online {\itercomp}.
  Because this version simulates a \textit{perfect} profiling, with zero overhead,
  it allows us isolate and evaluate the effectiveness work-efficiency metric.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real-world online scenario.
  The program is executed only once with each input.
  It uses the optimal work profiling for computing the work efficiency.
\item \textbf{Real-R5} is similar to the {Real-OP}, but with a relaxation of 5\% in the work profiling.
\item \textbf{Real-WPO-R5} is similar to the {Real-OP}, but with a whole-program relaxation of 5\% in the work profiling.
%\item \textbf{Real-IPC} uses IPC for guiding the online {\itercomp}.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.

Figure~\ref{fig:window-size} shows the average input-window size for each benchmark and configuration.
It shows that we can have a statistically sound measurement of the performance metric using just a small number of inputs.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/window-size.pdf}
    \caption{Average input-window sizes observed during the online {\itercomp}.}
    \label{fig:window-size}
\end{figure*}

>>>>

For comparison, we use five configurations.
In all configurations, the same optimization sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimization sequence across distinct inputs.
The optimization sequences are ranked based on their average performance, and the best optimization sequence is selected.
%When selecting the best optimization sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}[leftmargin=3mm]
\item \textbf{Oracle-RM} executes the program twice for each input, measuring the real speedup for each optimization sequence, and then uses the real speedup over {\flagstype -O0} for guiding online {\itercomp}. This oracle provides a reference results for assessing the effectiveness work-efficiency metric.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  It uses the work-efficiency metric for guiding online {\itercomp}.
  Because this version simulates a \textit{perfect} profiling, with zero overhead,
  it allows us isolate and evaluate the effectiveness work-efficiency metric.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real-world online scenario.
  The program is executed only once with each input.
  It uses the optimal work profiling for computing the work efficiency.
\item \textbf{Real-R5} is similar to the {Real-OP}, but with a relaxation of 5\% in the work profiling.
\item \textbf{Real-WPO-R5} is similar to the {Real-OP}, but with a whole-program relaxation of 5\% in the work profiling.
%\item \textbf{Real-IPC} uses IPC for guiding the online {\itercomp}.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.

%Figure~\ref{fig:window-size} shows the average input-window size for each benchmark and configuration.
%It shows that we can have a statistically sound measurement of the performance metric using just a small number of inputs.

%\begin{figure*}[t]
%    \centering
%    \includegraphics[width=\textwidth]{figs/window-size.pdf}
%    \caption{Average input-window sizes observed during the online {\itercomp}.}
%    \label{fig:window-size}
%\end{figure*}
